Bad forecast, good decision: what makes a model relevant for determining policy

### 2020-10-17 manuscript/manuscript.Rmd
:pen:

```{r plot_sims}
fig2a <- 
  sims %>%
  filter(time < 25, reps < 5) %>%
  ggplot(aes(time, state, col=model, group = interaction(model,reps))) + 
  geom_line(alpha=0.3) 
```

>>>>

```{r plot_sims}
fig2a <- 
  sims %>%
  filter(time < 25, reps < 5, model != 3) %>%
  ggplot(aes(time, state, col=model, group = interaction(model,reps))) + 
  geom_line(alpha=0.3) 
```
